Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2021-01-12 submission/NatCom_all_models.tex
last minute changes before resubmission

Results are summarized in Table~\ref{table:results} (and Figures~\ref{fig:summary_regressions_A}--\ref{fig:summary_regressions_I} of the Supplementary Material).
For the mean, 
smaller RMSE, 
larger $R^2$, and 
larger Kendal-$\tau$ 
are desirable; 
and, for the standard deviation, smaller values are desirable.
Taken as a whole, over the entire corpus of data, PL-based metrics are somewhat better for both the $R^{2}$ mean and standard deviation;
and PL-based metrics are much better for RMSE mean and standard deviation.
Model diagnostics (Supplementary Material) indicate many outliers and imperfect fits.
Overall, though, these and other results suggest our conclusions hold much more generally.

>>>>

Results are summarized in Table~\ref{table:results} (and Figures~\ref{fig:summary_regressions_A}--\ref{fig:summary_regressions_I} of the Supplementary Information).
For the mean, 
smaller RMSE, 
larger $R^2$, and 
larger Kendal-$\tau$ 
are desirable; 
and, for the standard deviation, smaller values are desirable.
Taken as a whole, over the entire corpus of data, PL-based metrics are somewhat better for both the $R^{2}$ mean and standard deviation;
and PL-based metrics are much better for RMSE mean and standard deviation.
Model diagnostics (Supplementary Information) indicate many outliers and imperfect fits.
Overall, though, these and other results suggest our conclusions hold much more generally.

### 2021-01-12 submission/NatCom_cv_models.tex
last minute changes before resubmission

In particular, the PL-based 
Weighted Alpha and Log $\alpha$-Norm
metrics tend to perform better when there is a wider variation in the hyperparameters, going beyond just increasing the depth.  
In addition, sometimes the purely norm-based metrics such as the Log Spectral norm can be uncorrelated or even anti-correlated with the test accuracy, while the PL-metrrics are positively-correlated.
This is seen in the Supplementary Material, 
ShuffleNet in Figure~\ref{fig:summary_regressions_B_02},
SqueezeNext in Figure~\ref{fig:summary_regressions_C_10}, and 
WRN in Figure~\ref{fig:summary_regressions_G_06}).

>>>>

In particular, the PL-based 
Weighted Alpha and Log $\alpha$-Norm
metrics tend to perform better when there is a wider variation in the hyperparameters, going beyond just increasing the depth.  
In addition, sometimes the purely norm-based metrics such as the Log Spectral norm can be uncorrelated or even anti-correlated with the test accuracy, while the PL-metrrics are positively-correlated.
This is seen in the Supplementary Information, 
ShuffleNet in Figure~\ref{fig:summary_regressions_B_02},
SqueezeNext in Figure~\ref{fig:summary_regressions_C_10}, and 
WRN in Figure~\ref{fig:summary_regressions_G_06}).

### 2021-01-12 submission/resp_to_revs_NatCom.tex
last minute changes before resubmission

\begin{quote}
%(((XXX.  CM: 
%The best thing is to run R2 and Ktau, not p-values, and then also look at the plots.
%I'm open to other suggestions here.
%I'll need to set this up this week, and also create a repo with ALL the plots.
%)))\\
The reviewer is correct.  
We intended for the reader to examine plots to see that the trends are qualitatively in the correct (or incorrect, in some cases for norm-based metrics) direction, and then to look at the numbers to get quantitative insight.
We know that errors are not normal; so, for this and other reasons, in our experience, reporting $p$-values won't clarify the situation.
Instead, to clarify understanding, we have expanded all of the tables that report RMSE and/or $R^2$ to report the Kendal-$\tau$ rank correlation measure; and we have provided figures in the Supplementary Material for all model-dataset pairs, which indicates trends more clearly than the aggregated data.
Also, a point we didn't emphasize enough is that from HT-SR theory we expect that PL-based metrics to have strong linear and not just rank correlation.
We have clarified these points 
in the text 
of the revised manuscript, and in the tables and plots throughout the manuscript.
(Also, additional results beyond what we have in the main text and Supplementary Material are available in our fully-reproducible and publicly-available repo, and it is our hope that that level of transparency will aid the reader's understanding.)
%XXX.  MM STILL TO REFINE THIS ANSWER.
\end{quote}

@@

As for For Figure 9, this should be read in light of Tables 7, 8, and 9, as well as the discussion in Sec 2.4.  
Our metrics for predicting trends in model quality perform well within a given architectural series, and we have discussed this in detail in the main text.
We also want to show that our general results hold for the hundreds of publicly-available CV and NLP models.
All of this is available in our publicly-available repo, and so we decided in the text and Supplementary Material to go with just a summary.
In the main text, we have R2, MSE, and Kendall-Tau; and in the appendix, we have more granular results for several model series.
Since Figure 9 partitions based on data and not model series, we think that it will likely confuse the reader, as opposed to presenting results for all model-dataset pairs, as we now do.
Thus, we removed it, and we will simply point to the publicly-available repo.
%
We have clarified these points
in the revised manuscript.

@@

\begin{quote}
%(((XXX.  CM:
%We can add a supplementary github repo.
%)))\\
We have removed those statements and only refer to the main text or the Supplementary Material.
We do point out, however, that we intend out results to be fully-reproducible by the community, and thus our publicly-available repo is designed to contain the enormous quantity of data underlying out analysis.
\end{quote}

>>>>

\begin{quote}
%(((XXX.  CM: 
%The best thing is to run R2 and Ktau, not p-values, and then also look at the plots.
%I'm open to other suggestions here.
%I'll need to set this up this week, and also create a repo with ALL the plots.
%)))\\
The reviewer is correct.  
We intended for the reader to examine plots to see that the trends are qualitatively in the correct (or incorrect, in some cases for norm-based metrics) direction, and then to look at the numbers to get quantitative insight.
We know that errors are not normal; so, for this and other reasons, in our experience, reporting $p$-values won't clarify the situation.
Instead, to clarify understanding, we have expanded all of the tables that report RMSE and/or $R^2$ to report the Kendal-$\tau$ rank correlation measure; and we have provided figures in the Supplementary Information for all model-dataset pairs, which indicate trends more clearly than the aggregated data, and which (among other things) show that the plots display the $95\%$ confidence band for every regression along with tabulated results for all metrics.
Also, a point we didn't emphasize enough is that from HT-SR theory we expect that PL-based metrics to have strong linear and not just rank correlation.
We have clarified these points 
in the text 
of the revised manuscript, and in the tables and plots throughout the manuscript.
(Also, additional results beyond what we have in the main text and Supplementary Information are available in our fully-reproducible and publicly-available repo, and it is our hope that that level of transparency will aid the reader's understanding.)
%XXX.  MM STILL TO REFINE THIS ANSWER.
\end{quote}

@@

As for (previous) Figure 9, this should be read in light of Tables 7, 8, and 9, as well as the discussion in Sec 2.4.  
Our metrics for predicting trends in model quality perform well within a given architectural series, and we have discussed this in detail in the main text.
We also want to show that our general results hold for the hundreds of publicly-available CV and NLP models.
All of this is available in our publicly-available repo, and so we decided in the text and Supplementary Information to go with just a summary.
In the main text, we have R2, MSE, and Kendall-Tau; and in the appendix, we have more granular results for several model series.
Since (previous) Figure 9 partitions based on data and not model series, we think that it will likely confuse the reader, as opposed to presenting results for all model-dataset pairs, as we now do.
Thus, we removed it, and we will simply point to the publicly-available repo.
%
We have clarified these points
in the revised manuscript.

@@

\begin{quote}
%(((XXX.  CM:
%We can add a supplementary github repo.
%)))\\
We have removed those statements and only refer to the main text or the Supplementary Information.
We do point out, however, that we intend out results to be fully-reproducible by the community, and thus our publicly-available repo is designed to contain the enormous quantity of data underlying out analysis.
\end{quote}
